### 2010-04-02 papers/icfp-2010-desc/paper_discussion.tex
Desc@ICFP: suppress line break before equations: we are at 11.5 pages
Desc@ICFP: uniformize titles.
Desc@ICFP: uniformize coding style
strat chat

As such, our type theory suffers from an inconsistency. Indeed, the
typing rule $\Bhab{\Set}{\Set}$ leads to Girard's paradox. We made
that choice for presentational convenience, as universe stratification
is orthogonal to our work. Nonetheless, our universe of description
stratifies naturally. Unsurprisingly, $\IDesc{\!}$ at level $l$ is of
type $\Set^{\blue{l+1}}$. Similarly, the interpretation of
$\IDesc{\!}$ at level $l$ is an object of type $\Set^{\blue{l}}$:

\[\stk{
\data \IDesc{\!}^{\blue{l}} (\Bhab{\V{I}}{\Set^{\blue{l+1}}}) : \Set^{\blue{l+1}} \where \ldots \\
\\
\idescop{\_\:}{}{}^{\blue{l}} : \PI{\V{I}}{\Set^{\blue{l+1}}} \IDesc{{\!}^{\blue{l}}\V{I}} \To (\V{I} \To \Set^{\blue{l}}) \To \Set^{\blue{l}}    \\
\ldots
}\]

The operations and examples developed in this paper stratify just as
well. We refer the reader to our Agda model. Further, we have coded
$\IDesc{\!}$ in itself and have proved the isomorphism between the
host and the embedded universes.

\subsection{Related Work}

>>>>

As such, our type theory suffers from an inconsistency. Indeed, the
typing rule $\Bhab{\Set}{\Set}$ leads to Girard's paradox. We made
that choice for presentational convenience, as universe stratification
is orthogonal to our work. Nonetheless, our universe of description
stratifies naturally. $\IDesc{\!}$ is self-encoding only in a
level-polymorphic sense.  Unsurprisingly, $\IDesc{\!}$ at level $l$ is
of type $\Set^{\blue{l+1}}$. Similarly, the interpretation of
$\IDesc{\!}$ at level $l$ is an object of type $\Set^{\blue{l}}$:
%
\[\stk{\begin{array}{@{}ll}
\IDesc{\!}^{\blue{l}} (\Bhab{\M{I}}{\Set^{\blue{l+1}}}) & :\Set^{\blue{l+1}} \\
\DVar{(\Bhab{\M{i}}{\M{I}})} &: \IDesc{\!}^{\blue{l}}{\M{I}} \\
\DConst{(\Bhab{\M{A}}{\Set^{\blue{l}}})} &:\IDesc{\!}^{\blue{l}}{\M{I}}       \\
\DProd{(\Bhab{\M{D}}{\IDesc{\!}^{\blue{l}}{\M{I}}})}{(\Bhab{\M{D}}{\IDesc{\!}^{\blue{l}}{\M{I}}})}
  & :\IDesc{\!}^{\blue{l}}{\M{I}}       \\
\DSigma{(\Bhab{\M{S}}{\Set^{\blue{l}}})}{(\Bhab{\M{D}}{\M{S}\To\IDesc{\!}^{\blue{l}}{\M{I}}})}
& : \IDesc{\!}^{\blue{l}}{\M{I}}  \\
\DPi{(\Bhab{\M{S}}{\Set^{\blue{l}}})}{(\Bhab{\M{D}}{\M{S}\To\IDesc{\!}^{\blue{l}}{\M{I}}})}
& : \IDesc{\!}^{\blue{l}}{\M{I}}  \\
\end{array}\smallskip \\
\idescop{\_\:}{}{}^{\blue{l}} : _{\PI{\V{I}}{\Set^{\blue{l+1}}}} \IDesc{{\!}^{\blue{l}}\V{I}} \To (\V{I} \To \Set^{\blue{l}}) \To \Set^{\blue{l}}    \\
\ldots
}
\]
Crucially, the types of data stored in an
\(\IDesc{\!}^{\blue{l}}{\M{I}}\) all live no higher---we may store an
\(I\) and a \(\Set^{\blue{l}}\) in a \(\Set^{\blue{l+1}}\).  The code
for \(\IDesc{\!}^{\blue{l}}{\M{I}}\) is an element of
\(\IDesc{\!}^{\blue{l+1}}{\Unit}\), so there is a spiral, not a cycle.
We have checked the construction using Agda's universe polymorphism,
coding $\IDesc{\!}$ in itself and have proving the isomorphism
between the host and the embedded universes.

\subsection{Related work}
